%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Archit}{Srivastava}{ \urlstyle{same}\href{http://github.com/eh2arch}{github.com/eh2arch} | \href{http://fb.co/archit.sri}{fb.co/archit.sri}\\
\href{mailto:archits@usc.edu}{archits@usc.edu} | 323.649.0492 | \href{mailto:arch.srivastava.2@gmail.com}{arch.srivastava.2@gmail.com}
}

\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Microsoft}
\descript{| Software Developer Intern }
\location{May 2015 – July 2015 | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Created an \textbf{AutoBVT tool} for service level functional BVT validation for the VLCM team
\item Reduced pre-production and production scenario testing times from \textbf{4 hours} to \textbf{10 minutes} and paved the way for weekly releases for the SwE team.
\item
Scalable and extensible architecture that allowed parallel execution of tests on configurable test scenarios across multiple environments. In production
\end{tightemize}
\sectionsep

\runsubsection{\href{http://precog.iiitd.edu.in/}{Precog, Research Group at IIIT Delhi}}
\descript{| Research Associate }
\location{May 2014 – Present | New Delhi, India}
%\vspace{\topsep}
Worked remotely with \textbf{\href{http://precog.iiitd.edu.in/people/pk/Home.html}{Prof Dr. Ponnurangam Kumaraguru}} to develop an enterprise tool for forensic analysis of social media data using big data technologies. The tool tracks and visualizes information from various social networks (Facebook, Twitter, Google+, Instagram, etc) to produce insights. Funded by \textbf{Department of Electronics and Information Technology, Government of India} and is actively being used by around 50+ national agencies.

%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{USC Information Sciences Institute}
\descript{| Student Researcher}
\location{Aug 2016 – Present | Los Angeles, CA}
Currently working with \textbf{Prof Kristina Lerman}, \textbf{Prof Emilio Ferrara} and \textbf{Prof Ponnurangam Kumaraguru} to analyse the emotions, sociability and demographics in Santa Monica, LA through various social networks.
\sectionsep

\runsubsection{USC Gamepipe Labs}
\descript{| Directed Research}
\location{Aug 2016 – Present | Los Angeles, CA}
Working with \textbf{Prof Scott Easley} to design video game levels through Deep Machine Learning
\sectionsep


\runsubsection{Gesture Recognition through Accelerometer Data}
\descript{| Undergrad. Research thesis}
\location{Sept 2015 – Mar 2016 | NIT Durgapur}
Low-training gesture recognition to recognize hand motion gestures through accelerometer data on mobile devices.
%\sectionsep

\section{Projects}
\runsubsection{Data Science For Social Good}
\descript{| Recovery groups identification}
\location{Mar 2016}
Automated identification and characterization of the presence of alcoholics|narcotics anonymous(AA|NA) recovery groups on social networking platforms.
\sectionsep

\runsubsection{Online Compiler Judge}
\descript{| NIT Durgapur}
\location{Jan 2015 – Feb 2016}
Built using \textbf{RoR} and \textbf{Docker.io} for hosting several college level international coding competitions in a kernel-level sandboxed environment for a variety of languages. Adopted by the CS department.
\sectionsep

\runsubsection{Virtual Assistant using CMUSphinx}
\descript{| Individual Project}
\location{Jan 2015}
Virtual desktop assistant created using CMUSphinx library which recognizes dedicated voice commands and translates them to user actions.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Awards} 
%\begin{tabular}{rll}
%2014	     & top 52/2500  & KPCB Engineering Fellow\\
%2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, %Cornell\\
%2013	     & National  & Jump Trading Challenge Finalist\\
%2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
%2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot %Tournament \\
%2011     & National & Indian National Mathematics Olympiad (INMO) Finalist %\\
%\end{tabular}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the %.cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage}%
\hfill
%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection[University of Southern California]{University of Southern\\ California}
\descript{Master's in Computer Science}
\location{Expected May 2018 | Los Angeles, CA}
Viterbi School of Engineering \\
Relevant Coursework: Artificial Intelligence, Algorithms
\sectionsep

\subsection[National Institute of Technology]{National Institute of \\ Technology}
\descript{BTech in Information Technology}
\location{May 2016 | Durgapur, West Bengal, India}
\location{ Cum. GPA: 9.04 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Coursework}
%\subsection{Graduate}
%
%\sectionsep
%
%\subsection{Undergraduate}
%Information Retrieval \\
%Operating Systems \\
%Artificial Intelligence + Practicum \\
%Functional Programming \\
%Computer Graphics + Practicum \\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
%Unix Tools and Scripting \\
%\sectionsep
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Advanced:}
C/C++ \textbullet{}   C\# \textbullet{} Ruby \textbullet{} JavaScript \textbullet{} HTML/CSS \textbullet{} Python\\ 
\location{Intermediate:}
Java \textbullet{} SQL \textbullet{} PHP \textbullet{} \LaTeX\ \\
\location{Basic:}
Shell \textbullet{} Assembly \\
\location{Platforms/Frameworks:}
Rails \textbullet{} Windows \textbullet{} Linux \textbullet{} Bootstrap \textbullet{} D3.js Library \textbullet{} CMUSphinx \textbullet{} Docker.io \textbullet{} Apache Storm \textbullet{} NLTK \textbullet{} Celery \\
\location{Tools:}
Git \textbullet{} Visual Studio \textbullet{} Eclipse \textbullet{} Adobe Photoshop CS4 \textbullet{} Matlab/Octave \textbullet{} MongoDB
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extra Curriculars}
\descript{2015 \& 2014 \& 2013}\location{ACM ICPC Regionals} Secured ranks 67\textsuperscript{th}/1521, 122\textsuperscript{nd}/1455, 229\textsuperscript{th}/1642\\\vspace{6pt}
\descript{Microsoft Certification}\location{C\# \& .NET Fundamentals}\vspace{6pt}
\descript{2013 – 2014}\location{Co-Founder | Design and Content Manager} \textbf{\href{http://findaway.in/}{Find A Way}} - student led registered NGO which aims to use technology to help the underprivileged\\\vspace{6pt}
\descript{2014}\location{Columnist at The ’Zine} a quarterly magazine concentrating on the youth



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 


\end{document}  \documentclass[]{article}
